A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex
conclusion

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefiting from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. We introduced a new
 pseudo energy model, both taking into account the nearest-neighbour energy model 
and, to account for geometrical discrepancies,  the isostericity of all base pairs.

By combining these two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 into \texttt{RNApyro}, we created a tool predicting the positions
 yielding sequencing error and their correct value.
We validated our model with the 5s rRNA,
as presented in Sec.~\ref{sec:results}.
We observed that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.

>>>>

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefiting from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. The algorithm runs in  $\Theta(n\cdot(|\Omega|+m^2))$ time and $\Theta(n\cdot(|\Omega|+m))$ memory, where $n$ is the length of the RNA,
$m$ the number of mutations and $\Omega$ the size of the multiple sequence alignment.

We additionally introduce a new
 pseudo energy model, both taking into account the nearest-neighbour energy model 
and, to account for geometrical discrepancies,  the isostericity of all base pairs.

By combining  into \texttt{RNApyro} these two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 we created a tool predicting the positions
 yielding point-wise sequencing error and correcting them.
We validated our model with the 5s rRNA,
as presented in Sec.~\ref{sec:results}.
We observed that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.
